Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-23 demystify.tex
updates

    {\fontsize{16}{19.2} \selectfont \textcolor{ForestGreen}{\bf ThanhVu (Vu) Nguyen}}\\[0.1in]
    George Mason University, Dept. of Computer Science\\[0.1in]
    \today{} (latest version available on  \href{https://github.com/nguyenthanhvuh/phd-cs-us}{Github})
    };
    \end{tikzpicture}

@@

\begin{center}
  \href{https://nguyenthanhvuh.github.io/phd-cs-us/demystify.pdf}{nguyenthanhvuh.github.io/phd-cs-us/demystify.pdf},
\end{center}

\noindent and its \LaTeX{} source is also on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{GitHub}. If you have questions or comments, feel free to create new \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issues} or \href{https://github.com/nguyenthanhvuh/phd-cs-us/discussions}{discussions}.

@@

This book also aims to explain the \textbf{reasons behind the admission process}.
There are numerous \href{https://github.com/nguyenthanhvuh/phd-cs-us}{resources online} that tell you \emph{``what''} to do, but few explain the \emph{``why''}, e.g., why LoRs matter so much, why you should not draft your own LoR, why you should contact professors, etc. Understanding the reason and mindset of the admission committee and profs. can help you prepare better.

@@

I started writing this book in May 2023 and have been updating it since then (mostly around deadline time when I procrastinate, i.e., \emph{productive procrastination}!). The book was initially intended for international students but has been updated to include domestic students (\autoref{chap:domestic-students} and \autoref{chap:fellowships}).
The book is open-source and available on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{GitHub} so that others can contribute to it.
\paragraph{About Me} I am an associate professor in the CS dept at George Mason University (Mason). Before Mason, I was at the University of Nebraska-Lincoln (UNL). Both UNL and Mason are large R1 research universities in the US and have many international students in their CS graduate programs. My personal and lab website is at \href{https://dynaroars.github.io}{dynaroars.github.io}.

>>>>

    {\fontsize{16}{19.2} \selectfont \textcolor{ForestGreen}{\bf ThanhVu (Vu) Nguyen}}\\[0.1in]
    George Mason University, Dept. of Computer Science\\[0.1in]
    \today{} (latest version available on  \href{https://github.com/dynaroars/phd-cs-us}{Github})
    };
    \end{tikzpicture}

@@

\begin{center}
  \href{https://dynaroars.github.io/phd-cs-us/demystify.pdf}{dynaroars.github.io/phd-cs-us/demystify.pdf},
\end{center}

\noindent and its \LaTeX{} source is also on \href{https://github.com/dynaroars/phd-cs-us}{GitHub}. If you have questions or comments, feel free to create new \href{https://github.com/dynaroars/phd-cs-us/issues}{GitHub issues} or \href{https://github.com/dynaroars/phd-cs-us/discussions}{discussions}.

@@

This book also aims to explain the \textbf{reasons behind the admission process}.
There are numerous \href{https://github.com/dynaroars/phd-cs-us}{resources online} that tell you \emph{``what''} to do, but few explain the \emph{``why''}, e.g., why LoRs matter so much, why you should not draft your own LoR, why you should contact professors, etc. Understanding the reason and mindset of the admission committee and profs. can help you prepare better.

@@

I started writing this book in May 2023 and have been updating it since then (mostly around deadline time when I procrastinate, i.e., \emph{productive procrastination}!). The book was initially intended for international students but has been updated to include domestic students (\autoref{chap:domestic-students} and \autoref{chap:fellowships}).
The book is open-source and available on \href{https://github.com/dynaroars/phd-cs-us}{GitHub} so that others can contribute to it.
\paragraph{About Me} I am an associate professor in the CS dept at George Mason University (Mason). Before Mason, I was at the University of Nebraska-Lincoln (UNL). Both UNL and Mason are large R1 research universities in the US and have many international students in their CS graduate programs. My personal and lab website is at \href{https://dynaroars.github.io}{dynaroars.github.io}.
